Deep Reinforcement Learning for Conservation Decisions

### 2021-09-29 manuscript/manuscript.Rmd
Touching up behav. eco paragraph; swapped order of next 2 paragraphs

>>>>

<!-- RL for behavioral ecology is not the same as RL for conservation -->
This paper does not set the precedent as the first application of RL to ecology.
There have been a number of studies applying RL to behavioral ecology, typically with multi-agent environments [@wang_reinforcement_2020, @frankenhuis_enriching_2019, @perolat_multi-agent_2017].
Yet, it is important to distinguish the aim of these behavioral studies from the aim of applying RL to conservation management.
In behavioral ecology studies, RL agents are used to represent organisms.
Assuming that animals attempt to maximize some cumulative reward like RL agents, the authors of these studies draw conclusions about animal behavior and evolution by observing how the RL agents perform.
When applying deep RL to conservation management, we do not make the assumption that the behavior of an RL agent is a good substitute for the behavior of an animal.
For conservation management, we instead propose using RL as a tool to search for solutions to unsolved decision-making problems.
